%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}
%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}


\usepackage[colorlinks]{hyperref}

\begin{document}

\name{ABHIRAM S}
\tagline{Cyber Security Engineer | Python | Network Security}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{ars.abhiram@gmail.com}
  \phone{+91 70347 18372}
%  \homepage{www.homepage.com}
%  \twitter{@twitterhandle}
  \linkedin{linkedin.com/in/abhiram-s-517b38281/}
  \github{github.com/Abhiram-ARS}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}


%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Intenship Experience}

\cvevent
    {Cyber Security Intern}
    {Kerala Police}
    {May 2026 - June 2026 (1 Month)}
    {Aluva, Kerala}
    \begin{itemize}
        \item Developed Call Detail Record (CDR) analysis tool.
        \item Performed detailed analysis of 2 real-world malware-based scam campaigns, evaluating attack techniques and security impacts.
        \item Participated in 3-Day cybercrime investigation training, gaining knowledge of digital forensics and evidence handling.

    \end{itemize}


\cvsection{Projects}

\cvevent
    {EduCredChain, A Hybrid Blockchain–PKI Architecture for Educational Credential Verification [BTech Mini Project]}
    {Team Size - 3, Role: Backend \& Blockchain Development}
    {December 2025 - May 2026}
    {}
    \begin{itemize}
        \item Engineered a hybrid Blockchain–PKI solution that reduced Ethereum gas consumption by ~79–82\% using a hybrid on-chain/off-chain architecture storing only SHA-256 hashes on-chain.
        \item Technologies Used: Python, FastAPI, Solidity, HTML/CSS/JavaScript, Ganache, Web3.py, SQLite, SHA-256, RSA Cryptography.
    \end{itemize}

\divider

\cvevent
    {CDR-IED, CDR Interpretation and Examination Dashboard}
    {Team Size - Individual}
    {May 2026 - June 2026}
    {}
    \begin{itemize}
        \item Developed a Call Detail Record (CDR) analysis dashboard to investigate call records, reducing manual effort during digital forensic investigations.
        \item Technologies Used: Python, HTML/CSS/JavaScript, SQLite.
    \end{itemize}

\cvsection{Achievements}

\begin{itemize}
    \item Class Topper for the 5th Semester among 30+ students
    \item 1st Place, Co-Coder 2.0 Code Debugging Competition, CSI SB ICET, competing against 50+ students.
    \item 3rd Place, State-Level Game Development Competition with 50+ participants.
    \item Completed 24 CTF challenges from various domains in TryHackMe Advent of Cyber 2025 alongside 2,000+ peers.
    \item Technical Coordinator, CodeStorm 2026, coding competition with 30+ Participants.
    \item Coordinator, PixelHack CTF Competition with 30+ Participants.
    \item Coordinator, Co-Coder 3.0 Competition with 30+ Participants.
    \item Resource Person for a Scratch Programming Workshop for 35+ students.
    
    
\end{itemize}

\cvsection{Positions Held}

\begin{itemize}
    \item Chairman, CSI ICET SB - 2026–27
    \item Website Co-Lead, Cyber Wing ICET - 2025-26
    \item Treasurer, CSI ICET SB - 2025–26
    \item Finance Co-Lead, GDC ICET - 2024-25

\end{itemize}

    

\end{document}
